The Inner Mass-Ratio Distribution of Intermediate-Mass Stars

### 2016-03-08 paper/ms.tex
Updated sections 1-3

In this paper, we describe a spectroscopic survey of nearby chemically normal, main sequence intermediate-mass stars ($M \approx 1.5 - 15 M_{\odot}$). We search for companions using the direct spectral detection technique \citep{Gullikson2016}, which has a separation-invariant detection rate for all separations inside $\sim 1 ''$. We describe the stellar sample and data used for the survey in Section \ref{sec:obs}, as well as the data reduction steps in the same section. Next, we describe the direct spectral detection method and tabulate the companion detections in Section \ref{sec:companions}. We estimate the mass and age of the primary stars in Section \ref{sec:sp}, and discuss the survey completeness in Section \ref{sec:completeness}. Finally, we end with a derivation of the mass-ratio distribution from our sample in Section \ref{sec:mrd} and discuss its implications for binary formation in Section \ref{sec:discussion}.

@@

The magnitude limit ensures that a sufficiently high signal-to-noise ratio can be achieved in a short period of time. It does introduce a Malmquist bias in the derived mass ratio, which we discuss and correct for in Section \ref{sec:mrd}. Likewise, the $v\sin{i}$ limit makes accounting for the primary star spectrum in the companion search trivial; since most A- or B-type stars are rapid rotators, the cutoff removes less than half of the stars from the potential sample. We exclude pre-main sequence stars because both the primary and the companion mass would depend very strongly on young and uncertain ($\lesssim 1$ Myr) evolutionary models. Finally, we exclude post-main sequence stars from our sample because the binary flux ratio would be even less favorable to companion detection in an evolved star. Most of the spectral peculiarities denote narrow lines, which are already removed from the sample by the $v\sin{i}$ cut. The sample is given in Table \ref{tab:sample}. The spectral type, coordinates, V magnitude, and parallax are all adopted from the Simbad Database \citep{Simbad}.

@@

IGRINS only has one setting with $R = 40000$. It has complete wavelength coverage from $1475-2480$ nm, except in the telluric water band from $1810 - 1930$ nm. Each star is observed in an ABBA nodding mode, and reduced using the standard IGRINS pipeline \citep{IGRINS_plp_v2}. The standard pipeline uses atmospheric OH emission lines as well as a Th-Ar calibration frame to calibrate the wavelengths; we further refine the wavelength solution using telluric absorption lines in the science spectrum.

@@

All of the reduced and telluric-corrected spectra used in this study will be released with this work, and will be available at the following url: \url{https://zenodo.org/record/46482}.

\subsection{Imaging Data}
As part of the follow-up effort, we used the NIRI instrument behind the Altair adaptive optics system at the Gemini North Telescope. For each star listed in Table \ref{tab:imaging_obs}, we obtained 25 images in 5 dithering positions. We used the K-continuum band centered on $2.2718\ \mu m$ and a variety of exposure times and dates (listed in Table \ref{tab:imaging_obs}). Because the targets are all extremely bright, we used the high read noise and high flux detector settings to allow for very short co-add exposure times. We reduced the data using the Gemini set of IRAF tasks, which include steps for nonlinearity correction, flat-fielding, sky subtraction, and co-addition of the dither frames.

@@

We have follow-up spectroscopy for 17/27 of the new companions to confirm their existence. In most cases, there is a clear shift in the radial velocity of the companion, indicating that it is orbiting the target star and is not a foreground or background contaminant (See Figure \ref{fig:ccf}). Two of the new detections (companions to HIPs 38593 and 79404) were detected twice but not in a third attempt, most likely because the third spectrum had low signal-to-noise. The companion to HIP 93805, at $\sim 4000$ K, was detected twice with near-infrared IGRINS but not the optical CHIRON instrument that is less sensitive to cool companions than IGRINS. Two of the companions with only one detection were observed at least twice (HIPs 19949 and HIP 23362); both of the non-detections are from the IGRINS instrument, which is less sensitive to hot companions with rapid rotation speeds because there are far fewer spectral lines of the companion in the near-infrared than there are in the optical.

In addition we obtained Gemini/NIRI adaptive optics imaging data for 18 of the northern companions, and were able to resolve 7 of them. We show the separation, position angle, and magnitude difference measurements in Table \ref{tab:imaging_obs}, and display the images in Figure \ref{fig:images}. We also derive the projected separation in AU and the companion mass from the images. We calculate the separation from the measured angular separation and the Hipparchos parallax \citep{Hipparchos}. We calculate the companion mass and uncertainties from 1000 samples of the magnitude difference measurement and the primary star mass, temperature, age, and radius (see Section \ref{sec:sp}). For each sample, we use a grid of Kurucz stellar model spectra \citep{Castelli2003}and the pysynphot code\footnote{pysynphot is a python code package to perform synthetic photometry, and is available at this url: \url{https://pypi.python.org/pypi/pysynphot}} to determine the companion temperature needed to replicate the observed magnitude difference. We estimate the companion radius by interpolating solar metallicity Dartmouth isochrones [CITE] from the companion temperature and system age sample. We convert the best temperature to a companion mass using the same isochrone grid. The masses derived from the imaging data have very large uncertainties because the primary star property estimates that they depend on are very uncertain.

>>>>

In this paper, we describe a spectroscopic survey of nearby chemically normal, main sequence intermediate-mass stars ($M \approx 1.5 - 15 M_{\odot}$). We search for companions using the direct spectral detection technique \citep{Gullikson2016}, which has a separation-invariant detection rate for all separations inside $\sim 1 ''$. We describe the stellar sample and data used for the survey in Section \ref{sec:obs}, as well as the data reduction steps in the same section. Next, we describe the direct spectral detection method and tabulate the companion detections in Section \ref{sec:companions}. We estimate the mass and age of the sample stars in Section \ref{sec:sp}, and discuss the survey completeness in Section \ref{sec:completeness}. Finally, we end with a derivation of the mass-ratio distribution from our sample in Section \ref{sec:mrd} and discuss its implications for binary formation in Section \ref{sec:discussion}.

@@

The magnitude limit ensures that a sufficiently high signal-to-noise ratio can be achieved in a short period of time. It does introduce a Malmquist bias in the derived mass ratio, which we discuss and correct for in Section \ref{sec:mrd}. Likewise, the $v\sin{i}$ limit makes accounting for the primary star spectrum in the companion search trivial; since most A- or B-type stars are rapid rotators, the cutoff removes less than half of the stars from the potential sample. We exclude pre-main sequence stars because both the primary and the companion mass would depend very strongly on young and uncertain ($\lesssim 1$ Myr) evolutionary models. Finally, we exclude post-main sequence stars from our sample because the binary flux ratio would be even less favorable to companion detection in an evolved star. Most of the spectral peculiarities denote narrow lines, which are already removed from the sample by the $v\sin{i}$ cut. The sample is given in Table \ref{tab:sample}. The spectral type, coordinates, V magnitude, and parallax are all adopted from the Simbad Database \citep{Simbad}, while the stellar effective tempreature, surface gravity, masses, and ages are discussed in Section \ref{sec:sp}.

@@

IGRINS has a single setting with $R = 40000$. It has complete wavelength coverage from $1475-2480$ nm, except in the telluric water band from $1810 - 1930$ nm. Each star is observed in an ABBA nodding mode, and reduced using the standard IGRINS pipeline \citep{IGRINS_plp_v2}. The standard pipeline uses atmospheric OH emission lines as well as a Th-Ar calibration frame to calibrate the wavelengths; we further refine the wavelength solution using telluric absorption lines in the science spectrum.

@@

\subsection{Imaging Data}
As part of the follow-up effort, we used the NIRI instrument behind the Altair adaptive optics system on the Gemini North Telescope. For each star listed in Table \ref{tab:imaging_obs}, we obtained 25 images in 5 dithering positions. We used the K-continuum band centered on $2.2718\ \mu m$ and a variety of exposure times and dates (listed in Table \ref{tab:imaging_obs}). Because the targets are all extremely bright, we used the high read noise and high flux detector settings to allow for very short co-add exposure times. We reduced the data using the Gemini set of IRAF tasks, which include steps for nonlinearity correction, flat-fielding, sky subtraction, and co-addition of the dither frames.

@@

We have follow-up spectroscopy for 15/23 of the new companions to confirm their existence. In most cases, there is a clear shift in the radial velocity of the companion, indicating that it is orbiting the target star and is not a foreground or background contaminant (See Figure \ref{fig:ccf}). Two of the new detections (companions to HIPs 38593 and 79404) were detected twice but not in a third attempt, most likely because the third spectrum had low signal-to-noise. The companion to HIP 93805, at $\sim 4000$ K, was detected twice with near-infrared IGRINS but not the optical CHIRON instrument that is less sensitive to cool companions than IGRINS. Two of the companions with only one detection were observed at least twice (HIPs 19949 and HIP 23362); both of the non-detections are from the IGRINS instrument, which is less sensitive to hot companions with rapid rotation speeds because there are far fewer spectral lines of the companion in the near-infrared than there are in the optical.

In addition to the spectroscopic follow-up, we obtained Gemini/NIRI adaptive optics imaging data for 18 of the northern companions, and were able to resolve 7 of them. We show the separation, position angle, and magnitude difference measurements in Table \ref{tab:imaging_obs}, and display the images in Figure \ref{fig:images}. We also derive the projected separation in AU and the companion mass from the images. We calculate the separation from the measured angular separation and the Hipparchos parallax \citep{Hipparchos}. We calculate the companion mass and uncertainties from 1000 samples of the magnitude difference measurement and the primary star mass, temperature, age, and radius (see Section \ref{sec:sp}). For each sample, we use a grid of Kurucz stellar model spectra \citep{Castelli2003}and the pysynphot code\footnote{pysynphot is a python package to perform synthetic photometry, and is available at this url: \url{https://pypi.python.org/pypi/pysynphot}} to determine the companion temperature needed to replicate the observed magnitude difference. We estimate the companion radius by interpolating solar metallicity Dartmouth isochrones [CITE] from the companion temperature and system age sample. We convert the best temperature to a companion mass using the same isochrone grid. The masses derived from the imaging data have very large uncertainties because the primary star property estimates that they depend on are very uncertain. The imaging masses agree with the spectroscopically-derived masses in Table \ref{tab:companions}, with the exception of HIP 115115 which has a much higher mass from the imaging data than the spectroscopic data. The spectroscopic masses for all stars are more reliable, since they are less model-dependent.
